Investigating the impacts of COVID-19 on team wins and social media engagement in the EPL and Manchester United

### 2022-04-27 outputs/paper/paper.Rmd
This commit is to make sure that everything is up to date so nothing is lost till this point.

---
title: "My title"
subtitle: "My subtitle if needed"
author:"Swarnadeep Chattopadhyay" 
thanks: "Code and data are available at: https://github.com/WanteXecutioN/Final_Project."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The recent developments of the COVID-19 pandemic has had a tremendous impact on the world. Albeit school, work or daily life, there has been changes to the way that we conduct our daily lives. While a lot has changed, the intensity of the major soccer competitions all around the world has not. With teams playing on a regular schedule with advanced COVID protocols, we wanted to assess if teams in the English Premier League have been severely impacted by the change in environment. This report investigates the impact of COVID from the standpoint of team wins and team engagement in the English Premier League(EPL)."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

\tableofcontents
\normalsize
\break

@@

# 1 Introduction
The English Premier League is renowned to be one of the most watched soccer leagues in the world. To date, the league is broadcasted in over 200 countries which spans over 4 billion people (Richard,2020). With such a large market, teams in the EPL are continually able to attract some of the best players in the world. This is pivotal because, not only will the league be attracting more engagement, but the level of competition will be more intense. At the start of 2020, the COVID-19 pandemic has halted a lot of major activities around the world. With the virus spreading quick, the organizers of the EPL halted premier league football between March to April. After the initial suspension of games, teams were allowed to play again but with no attendance and stricter protocols. As a group, we chanced upon an article on ESPN, that essentially highlights the loss of home advantage arising from games with no fans. Pivotally, they pointed out that Liverpool, who were the previous season winners, had lost 3 games at home during the COVID era. Prior to that, they were on a 68 games win streak at home (Hamilton, 2021).

# 2 Scope of the Report
We wanted to assess what we deem here, as the "COVID Effect", while builds on the fundamental impact that COVID has had on teams in the EPL. With that, our research questions are:

@@

Central to this investigation, we have chosen to use Manchester United because they are to date, the 4th most valuable club in the world at US$4.2 Billion. In the EPL, they are currently the most valuable club. A big part of the reason behind this valuation is, in the early 2000's, Manchester United had been one of the most dominant teams in the EPL, consistently ranking 1st in the league. In that time span, they have generated a large following in person and on social media.

# 3   Exploratory Data Analysis
This investigation will consist of 5 data sets and focus on teams in Premier League (in England). To assess the first question, we will be working with data sets 1-2. For reference, the 2019/2020 season will be associated with Pre-Covid period and 2020/2021 season will be associated with COVID period and the average season has 38 games.

## 3.1 Team Wins Data Analysis (1st Question)
```{r, echo=FALSE, results='hide'}
## Data from the Premier League in the 2019/2020 and 2020/2021 Season
early <- read.csv("C:/Users/dylan/OneDrive/Desktop/1920.csv")
later <- read.csv("C:/Users/dylan/OneDrive/Desktop/2021.csv")
summary(early)
summary(later)
```
```{r,echo=FALSE, results='hide'}
## Assigning attendance according to 1st and 3rd quartile. 
early %>% mutate(attendance = case_when(Attendance <= 21755 ~ 'Low',
                                      Attendance > 21756 & Attendance <= 38312 ~ 'Medium',
                                      Attendance > 38400 ~ 'High')) %>% mutate(prop= W/MP) -> early1

## Classification of attendance according to no fans and some fans
later %>% mutate(attendance1 = case_when(Attendance == 0 ~ 'None',
                                      Attendance > 0 ~ 'Yes')) %>% mutate(prop=W/MP) -> later1
```

@@

With the 2020/2021 season, the average goals scored by home team stands is: 38 goals or 1.31 goal per game. With the 1.31 goal per game, the average number of wins is 38%! Mean attendance in the 2020/2021 season stands at a mere 82.
Note here that, the 2020/2021 season is not finished, the average wins and average goals were computed over 29 games.

@@

## 3.2 Twitter Engagement Analysis for Manchester United (2nd Question)

```{r, echo=FALSE, results='hide'}
## Undivided twitter data for Manchester United
twitter_engagement <- read.csv("C:/Users/dylan/OneDrive/Desktop/Twitter-Engagement-Pre-PostCovid.csv",stringsAsFactors=FALSE)
## Division 1: Pre Covid = July-Dec 2019 total engagements
posts_2019 <- twitter_engagement %>% filter(Year.Month >= 2019, Year.Month < 2020)
total_engagements_2019 <- posts_2019 %>% group_by(Year.Month) %>% summarise(Total.engagements=sum(Total.engagements))
## Division 2: During COVID = Jan-June 2020 (2019/2020 Season)
posts_JanJune2020 <- twitter_engagement %>% filter(Year.Month >= 2020)
total_engagements_JanJune2020 <- posts_JanJune2020 %>% group_by(Year.Month) %>% summarise(Total.engagements=sum(Total.engagements))
## Division 3: During COVID = July-December 2020 (2020/2021 season)
twitter_postsJulyDec2020 <- read.csv("C:/Users/dylan/OneDrive/Desktop/Twitter-EngagementJuly-Dec2020.csv", stringsAsFactors=FALSE)
twitter_postsJD2020 <- twitter_postsJulyDec2020 %>% filter(Year.Month < 2021)
total_engagements_JulyDec2020 <- twitter_postsJD2020 %>% group_by(Year.Month) %>% summarise(Total.engagements=sum(Total.engagements))
total_engagements_2019
total_engagements_JanJune2020
total_engagements_JulyDec2020
```
3rd data set is the twitter engagement data for Manchester United. To clear up the data to account for periods of COVID, we have divided the data set into 3.

@@

# 4 Results and Methodology

## 4.1 Methodology
To answer the first question, we will aim to predict the expected wins of the teams using logistic regression. The dependent variable will be "prop" which is the proportion of Wins with respect to MP (formula = W/MP). The key differentiate of the two data set is trivially the huge loss of the fans, we want to include that as a key variable along with variables: GF, GA, Points + attendance. Here attendance is mutated to be categorical variables (low,medium and high) which we assigned according to the summary statistics (25%, 50%, 75%). On top of the regression, we will also use the Pythagorean formula to predict wins given the number of goals scored. By the end, we will assess the validity of both predictions.

@@

## 4.2 Aanlytic 1: Results from Team Wins affected by COVID

@@

### 4.2.1 Pythagorean Analysis
```{r,echo=FALSE}
##Predictions (Pythagorean) from the 19/20 season
earlyf <- early.fitted %>% mutate(wpct= (GF)^2/((GF)^2+(GA)^2)) %>% mutate(expwin = round(wpct*as.double(MP))) %>% arrange(desc(expwin)) 
bottomhalf <- earlyf %>% slice(10:20)
upperhalf <- earlyf %>% slice(1:10)
earlyf1 <- earlyf %>% slice(1:6)
early12 <- earlyf %>% mutate(GF=GF+0.5) %>% mutate(GA=GA+0.5) 
early1.2 <- fitdist(early12$GF, "weibull")
##Mutating data to account for the weibull estimates
early12 <- early12 %>% mutate(GFpg= GF/MP) %>% mutate(PPw = (2* GFpg)/2.951111)
head(early12)
```

@@

## 4.3 Analytic 2: Twitter Engagement

### 4.3.1 Pre Covid Engagement
```{r,echo=FALSE}
posts_2019 <- twitter_engagement %>% filter(Year.Month >= 2019, Year.Month < 2020)
## REGRESSION FOR PREDICTING PRE COVID 2019/2020 SEASON
t1 <- lm(Engagements.per.post~  Year.Month + Week.Day + Page.Likes, data= posts_2019)
## REGRESSION FOR PREDICTING DURING COVID 2019/2020 SEASON
t2 <- lm(Engagements.per.post ~ Year.Month + Week.Day + Page.Likes, data= posts_JanJune2020)
## Manchester United Team Data
PRECOVID <- read.csv("C:/Users/dylan/OneDrive/Desktop/wins1920.csv", stringsAsFactors=FALSE)
PRECOVID %>% filter(Attendance>0) %>% filter(Comp == "Premier League") -> MU1
## Obtains summary of average engagements
MU1e <- posts_2019 %>% 
  group_by(Year.Month) %>% 
  summarise(total = 
sum(Total.engagements), num.posts=n(),averageEng=total/num.posts) %>% slice(2:6)
## Obtains the average Wins
MU11 <- MU1 %>% 
  group_by(Year.Month) %>% 
  summarise(TotalW = sum(Result=="W"), ngames = n(), averageW = round(TotalW/ngames,2)) %>% slice(1:5)
## Creates the data frame required for comparison
Year.Month <- c("2019-08", "2019-09", "2019-10", "2019-11", "2019-12")
AverageEngagements <- c(174896, 101050, 108980, 112641, 161911)
AverageWins <- c(0.25, 0.33, 0.33,0.33, 0.57)
MUd <- data.frame(Year.Month, AverageEngagements, AverageWins)
MUd 
```

@@

### 4.3.2 During COVID Engagement
```{r,echo=FALSE}
## REGRESSION FOR PREDICTING ENGAGEMENT PER POST in 2020/2021 SEASON (DURING COVID)
t3 <- lm(Engagements.per.post~ Year.Month + Week.Day + Page.Likes, data= twitter_postsJulyDec2020)
## Reads in the current season's data for Manchester United
comp <- read.csv("C:/Users/dylan/OneDrive/Desktop/comp.csv",stringsAsFactors=FALSE) %>% filter(Comp =="Premier League")
## Obtains the Average Engagement for this season
MU1p <- twitter_postsJulyDec2020 %>% 
  group_by(Year.Month) %>% 
  summarise(totalw = 
sum(Total.engagements), numposts=n(),averageE=totalw/numposts) %>% slice(3:9)
## Summary by Average Wins
MU22 <- comp %>% 
  group_by(Year.Month) %>% 
  summarise(TotalWi = sum(Result=="W"), nugames = n(), averageWi = TotalWi/nugames) %>% slice(2:8)
## Creation of data frame 
Year.Month <- c("2020-09", "2020-10", "2020-11", "2020-12", "2021-01", "2021-02", "2021-03")
AverageEngagementsCOVID <- c(214998, 279741, 163609, 205917, 281107, 231911, 182677)
AverageWinsCOVID <- c(0.5, 0.33, 1,0.67, 0.50,0.40,0.67)
MUCOVID <- data.frame(Year.Month, AverageEngagementsCOVID, AverageWinsCOVID)
MUCOVID
```
A similar tale. The number of average engagements on Twitter (per post) has no real effect on the average wins. Manchester United had the highest average wins (100%) when the average engagement was the lowest (163609). To support, when average engagements was the highest at 281107, the average wins was only 0.50 (50%)

### 4.3.3 Difference in Average Engagements vs Predicted Engagement
```{r,echo=FALSE}
## OBTAINS DATA FRAME REQUIRED FOR COMPARISON
MUd %>% slice(2:5) -> MUd
MUCOVID %>% slice(1:4) -> MUCOVID
Month <- c("September", "October", "November", "December")
ChangeInEngagements <- c(113948, 170761, 50968, 44006)
ChangeInWinsPerc <- c(0.17, 0,0.67,0.1)
ChangeDataFrame <- data.frame(Month, ChangeInEngagements, ChangeInWinsPerc)
twitter_postsJulyDec2020 %>% mutate(ExpectedEngPerPost = round(fitted(t3),2)) %>% mutate(ExtraEngPerPost = Engagements.per.post-ExpectedEngPerPost) -> twit
twit %>% group_by(Year.Month) %>% summarise(TotalEPP = sum(ExpectedEngPerPost), count=n(), AVG = TotalEPP/count) -> twit1
twit1 %>% slice(3:6) -> twit1
posts_2019 %>% mutate(EEPP = round(fitted(t1),2)) %>% mutate(ExTPP = Engagements.per.post-EEPP) -> twitprecovid
twitprecovid %>% group_by(Year.Month) %>% summarise(TEPP = sum(EEPP), count=n(), AVGE= TEPP/count) -> twit2 
twit2 %>% slice(3:6) -> twit2
Months <- c("September","October","November","December")
ACT <- c(113948,170761,50968,44006)
data.frame(Months,ACT, cbind(twit1,twit2)) -> Df 
Df %>% mutate(DiffAVG = AVG-AVGE) %>% mutate(OFF = ACT-DiffAVG) -> Df
Df
```
The main points from this comparison is to observe the predicted engagement per post vs the actual engagement per post. Here AVG, represents the predicted engagement per post during COVID and AVGE represents the predicted engagement per post PRE COVID. If we observe the extra engagement, the OFF column suggests that a very high deviance between the predicted engagement and actual engagement. We would expect to see some deviance in the plot.

## 4.4 Visual 2: Change in Engagement vs Change in Actual Win%
```{r,echo=FALSE}
ggplot(Df, aes(Months,OFF,fill=ACT ,colour=ACT)) + 
  geom_bar(stat = 'identity', position = 'identity') +
  coord_flip() +
  theme_minimal() +
  guides(fill = 'none') +
  xlab('') + ylab('Difference between Actual Engagement vs Predicted Engagement')+
  ggtitle("Pre vs During COVID changes in Actual vs Predicted Engagement") -> gg
ggplot(ChangeDataFrame, aes(x=ChangeInEngagements)) + geom_line(aes(y=ChangeInWinsPerc),color="red") + geom_text(aes(y=0.67,x=58000),label = "Peak") + geom_text(aes(y=0.05, x=171000), label="Worst")+ ggtitle("Pre vs During COVID changes in Actual Win% given Changes in Engagement") -> ggwp
grid.arrange(gg,ggwp, nrow=2)
```

@@

# 5 Conclusion
The premise of this paper was to:
1) investigate the effect of COVID on team wins in the EPL
2) investigate the effect of COVID on team engagement (MANCHESTER UNITED) in the EPL

>>>>

---
title: "Investigating the impacts of COVID-19 on team wins and social media engagement in the EPL and Manchester United"
author: "Swarnadeep Chattopadhyay" 
thanks: "Code and data are available at: https://github.com/WanteXecutioN/Final_Project."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The recent developments of the COVID-19 pandemic has had a tremendous impact on the world. Albeit school, work or daily life, there has been changes to the way that we conduct our daily lives. While a lot has changed, the intensity of the major soccer competitions all around the world has not. With teams playing on a regular schedule with advanced COVID protocols, we wanted to assess if teams in the English Premier League have been severely impacted by the change in environment. This report investigates the impact of COVID from the standpoint of team wins and team engagement in the English Premier League(EPL) and uses Manchester United which is a club playing the league to prove the point. @citeR is the software used to perform this analysis. "
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

\tableofcontents
\normalsize

@@

# Introduction
The English Premier League is renowned to be one of the most watched soccer leagues in the world. To date, the league is broadcasted in over 200 countries which spans over 4 billion people (@citeRichards). With such a large market, teams in the EPL are continually able to attract some of the best players in the world. This is pivotal because, not only will the league be attracting more engagement, but the level of competition will be more intense. At the start of 2020, the COVID-19 pandemic had halted a lot of major activities around the world. With the virus spreading quick, the organizers of the EPL halted the premier league football between March to June. After the initial suspension of the games, teams were allowed to play again but behind closed doors meaning no attendance and stricter protocols. We chanced upon an article on ESPN, that essentially highlights the loss of home advantage arising from games with no fans. Pivotally, they pointed out that Liverpool, who were the 2019-2020 season winners, had lost 6 games at home during the COVID era. Prior to that, they were on a 68 games win streak at home (@citeHamilton). We use @citetidyverse, @citegridExtra, @citehrbrthemes, @citefitdistrplus, @citereadxl and @citerms to prove how Covid has affected teams in the EPL both on and off the field.

# Scope of the Report
We wanted to assess what we deem here, as the "COVID Effect", while building on the fundamental impact that COVID has had on teams in the EPL. With that, our research questions are:

@@

Central to this investigation, we have chosen to use Manchester United because they are to date, the 4th most valuable club in the world at US$4.2 Billion. In the EPL, they are currently the most valuable club. A big part of the reason behind this valuation is, in the early 2000's, Manchester United had been one of the most dominant teams in the EPL, consistently ranking 1st in the league. In that time span, they have generated a large following in person and on social media. The team has fans living all around the world who constantly contribute by purchasing the team's merchandise.

# Data Collection

In terms of collecting the data, there were numerous websites used to conduct this paper. Firstly, the 2019-2020 season data was generated from @cite19-20.

# Exploratory Data Analysis
This investigation will consist of 5 data sets and focus on teams in Premier League (in England). To assess the first question, we will be working with data sets 1-2. For reference, the 2019/2020 season will be associated with Pre-Covid period and 2020/2021 season will be associated with COVID period and the average season has 38 games.

## Team Wins Data Analysis (1st Question)
```{r, echo=FALSE, results='hide'}
## Data from the Premier League in the 2019/2020 and 2020/2021 Season
early <- read.csv("C:/Users/deeps/Desktop/STA304 Final project/1920.csv")
later <- read.csv("C:/Users/deeps/Desktop/STA304 Final project/2021.csv")
summary(early)
summary(later)
```
```{r,echo=FALSE, results='hide'}
## Assigning attendance according to 1st and 3rd quartile.
early %>% mutate(attendance = case_when(Attendance <= 21755 ~ 'Low',
                                      Attendance > 21756 & Attendance <= 38312 ~ 'Medium',
                                      Attendance > 38400 ~ 'High')) %>% mutate(prop= W/MP) -> early1

## Classification of attendance according to no fans and some fans
later %>% mutate(attendance1 = case_when(Attendance < 250 ~ 'Very Few',
                                      Attendance > 250 ~ 'Some')) %>% mutate(prop=W/MP) -> later1
```

@@

With the 2020/2021 season, the average goals scored by home team stands is: 38 goals or 1.31 goal per game. With the 1.31 goal per game, the average number of wins is 38%! Mean attendance in the 2020/2021 season stands at a mere 82.
Note here that, the 2020/2021 season is not finished, the average wins and average goals were computed over 29 games. (Change)

@@

## Twitter Engagement Analysis for Manchester United (2nd Question)

```{r, echo=FALSE, results='hide'}
## Undivided twitter data for Manchester United
twitter_engagement <- read.csv("C:/Users/deeps/Desktop/STA304 Final project/Twitter-Engagement-Pre-PostCovid.csv",stringsAsFactors=FALSE)
## Division 1: Pre Covid = July-Dec 2019 total engagements
posts_2019 <- twitter_engagement %>% filter(Year.Month >= 2019, Year.Month < 2020)
total_engagements_2019 <- posts_2019 %>% group_by(Year.Month) %>% summarise(Total.engagements=sum(Total.engagements))
## Division 2: During COVID = Jan-June 2020 (2019/2020 Season)
posts_JanJune2020 <- twitter_engagement %>% filter(Year.Month >= 2020)
total_engagements_JanJune2020 <- posts_JanJune2020 %>% group_by(Year.Month) %>% summarise(Total.engagements=sum(Total.engagements))
## Division 3: During COVID = July-December 2020 (2020/2021 season)
twitter_postsJulyDec2020 <- read.csv("C:/Users/deeps/Desktop/STA304 Final project/Twitter-EngagementJuly-Dec2020.csv", stringsAsFactors=FALSE)
twitter_postsJD2020 <- twitter_postsJulyDec2020 %>% filter(Year.Month < 2021)
total_engagements_JulyDec2020 <- twitter_postsJD2020 %>% group_by(Year.Month) %>% summarise(Total.engagements=sum(Total.engagements))
total_engagements_2019
total_engagements_JanJune2020
total_engagements_JulyDec2020
```
3rd data set is the twitter engagement data for Manchester United. To clear up the data to account for periods of COVID, we have divided the data set into 3.

@@

# Results and Methodology

## Methodology
To answer the first question, we will aim to predict the expected wins of the teams using logistic regression. The dependent variable will be "prop" which is the proportion of Wins with respect to MP (formula = W/MP). The key differentiate of the two data set is trivially the huge loss of the fans, we want to include that as a key variable along with variables: GF, GA, Points + attendance. Here attendance is mutated to be categorical variables (low,medium and high) which we assigned according to the summary statistics (25%, 50%, 75%). On top of the regression, we will also use the Pythagorean formula to predict wins given the number of goals scored. By the end, we will assess the validity of both predictions.

@@

## Aanlytic 1: Results from Team Wins affected by COVID

@@

### Pythagorean Analysis
```{r,echo=FALSE}
##Predictions (Pythagorean) from the 19/20 season
earlyf <- early.fitted %>% mutate(wpct= (GF)^2/((GF)^2+(GA)^2)) %>% mutate(expwin = round(wpct*as.double(MP))) %>% arrange(desc(expwin)) 
bottomhalf <- earlyf %>% slice(10:20)
upperhalf <- earlyf %>% slice(1:10)
earlyf1 <- earlyf %>% slice(1:6)
early12 <- earlyf %>% mutate(GF=GF+0.5) %>% mutate(GA=GA+0.5) 
early1.2 <- fitdist(early12$GF, "weibull")
##Mutating data to account for the weibull estimates
early12 <- early12 %>% mutate(GFpg= GF/MP) %>% mutate(PPw = (2* GFpg)/2.951111)
head(early12)
```

@@

## Analytic 2: Twitter Engagement

### Pre Covid Engagement
```{r,echo=FALSE}
posts_2019 <- twitter_engagement %>% filter(Year.Month >= 2019, Year.Month < 2020)
## REGRESSION FOR PREDICTING PRE COVID 2019/2020 SEASON
t1 <- lm(Engagements.per.post~  Year.Month + Week.Day + Page.Likes, data= posts_2019)
## REGRESSION FOR PREDICTING DURING COVID 2019/2020 SEASON
t2 <- lm(Engagements.per.post ~ Year.Month + Week.Day + Page.Likes, data= posts_JanJune2020)
## Manchester United Team Data
PRECOVID <- read.csv("C:/Users/deeps/Desktop/STA304 Final project/wins1920.csv", stringsAsFactors=FALSE)
PRECOVID %>% filter(Attendance>0) %>% filter(Comp == "Premier League") -> MU1
## Obtains summary of average engagements
MU1e <- posts_2019 %>% 
  group_by(Year.Month) %>% 
  summarise(total = 
sum(Total.engagements), num.posts=n(),averageEng=total/num.posts) %>% slice(2:6)
## Obtains the average Wins
MU11 <- MU1 %>% 
  group_by(Year.Month) %>% 
  summarise(TotalW = sum(Result=="W"), ngames = n(), averageW = round(TotalW/ngames,2)) %>% slice(1:5)
## Creates the data frame required for comparison
Year.Month <- c("2019-08", "2019-09", "2019-10", "2019-11", "2019-12")
AverageEngagements <- c(174896, 101050, 108980, 112641, 161911)
AverageWins <- c(0.25, 0.33, 0.33,0.33, 0.57)
MUd <- data.frame(Year.Month, AverageEngagements, AverageWins)
MUd 
```

@@

### During COVID Engagement
```{r,echo=FALSE}
## REGRESSION FOR PREDICTING ENGAGEMENT PER POST in 2020/2021 SEASON (DURING COVID)
t3 <- lm(Engagements.per.post~ Year.Month + Week.Day + Page.Likes, data= twitter_postsJulyDec2020)
## Reads in the current season's data for Manchester United
comp <- read.csv("C:/Users/deeps/Desktop/STA304 Final project/comp.csv",stringsAsFactors=FALSE) %>% filter(Comp =="Premier League")
## Obtains the Average Engagement for this season
MU1p <- twitter_postsJulyDec2020 %>% 
  group_by(Year.Month) %>% 
  summarise(totalw = 
sum(Total.engagements), numposts=n(),averageE=totalw/numposts) %>% slice(3:9)
## Summary by Average Wins
MU22 <- comp %>% 
  group_by(Year.Month) %>% 
  summarise(TotalWi = sum(Result=="W"), nugames = n(), averageWi = TotalWi/nugames) %>% slice(2:8)
## Creation of data frame 
Year.Month <- c("2020-09", "2020-10", "2020-11", "2020-12", "2021-01", "2021-02", "2021-03")
AverageEngagementsCOVID <- c(214998, 279741, 163609, 205917, 281107, 231911, 182677)
AverageWinsCOVID <- c(0.5, 0.33, 1,0.67, 0.50,0.40,0.67)
MUCOVID <- data.frame(Year.Month, AverageEngagementsCOVID, AverageWinsCOVID)
MUCOVID
```
A similar tale. The number of average engagements on Twitter (per post) has no real effect on the average wins. Manchester United had the highest average wins (100%) when the average engagement was the lowest (163609). To support, when average engagements was the highest at 281107, the average wins was only 0.50 (50%)

### Difference in Average Engagements vs Predicted Engagement
```{r,echo=FALSE}
## OBTAINS DATA FRAME REQUIRED FOR COMPARISON
MUd %>% slice(2:5) -> MUd
MUCOVID %>% slice(1:4) -> MUCOVID
Month <- c("September", "October", "November", "December")
ChangeInEngagements <- c(113948, 170761, 50968, 44006)
ChangeInWinsPerc <- c(0.17, 0,0.67,0.1)
ChangeDataFrame <- data.frame(Month, ChangeInEngagements, ChangeInWinsPerc)
twitter_postsJulyDec2020 %>% mutate(ExpectedEngPerPost = round(fitted(t3),2)) %>% mutate(ExtraEngPerPost = Engagements.per.post-ExpectedEngPerPost) -> twit
twit %>% group_by(Year.Month) %>% summarise(TotalEPP = sum(ExpectedEngPerPost), count=n(), AVG = TotalEPP/count) -> twit1
twit1 %>% slice(3:6) -> twit1
posts_2019 %>% mutate(EEPP = round(fitted(t1),2)) %>% mutate(ExTPP = Engagements.per.post-EEPP) -> twitprecovid
twitprecovid %>% group_by(Year.Month) %>% summarise(TEPP = sum(EEPP), count=n(), AVGE= TEPP/count) -> twit2 
twit2 %>% slice(3:6) -> twit2
Months <- c("September","October","November","December")
ACT <- c(113948,170761,50968,44006)
data.frame(Months,ACT, cbind(twit1,twit2)) -> Df 
Df %>% mutate(DiffAVG = AVG-AVGE) %>% mutate(OFF = ACT-DiffAVG) -> Df
Df
```
The main points from this comparison is to observe the predicted engagement per post vs the actual engagement per post. Here AVG, represents the predicted engagement per post during COVID and AVGE represents the predicted engagement per post PRE COVID. If we observe the extra engagement, the OFF column suggests that a very high deviance between the predicted engagement and actual engagement. We would expect to see some deviance in the plot.

## Visual 2: Change in Engagement vs Change in Actual Win%
```{r,echo=FALSE}
ggplot(Df, aes(Months,OFF,fill=ACT ,colour=ACT)) + 
  geom_bar(stat = 'identity', position = 'identity') +
  coord_flip() +
  theme_minimal() +
  guides(fill = 'none') +
  xlab('') + ylab('Difference between Actual Engagement vs Predicted Engagement')+
  ggtitle("Pre vs During COVID changes in Actual vs Predicted Engagement") -> gg
ggplot(ChangeDataFrame, aes(x=ChangeInEngagements)) + geom_line(aes(y=ChangeInWinsPerc),color="red") + geom_text(aes(y=0.67,x=58000),label = "Peak") + geom_text(aes(y=0.05, x=171000), label="Worst")+ ggtitle("Pre vs During COVID changes in Actual Win% given Changes in Engagement") -> ggwp
grid.arrange(gg,ggwp, nrow=2)
```

@@

# Conclusion
The premise of this paper was to:
1) investigate the effect of COVID on team wins in the EPL
2) investigate the effect of COVID on team engagement (MANCHESTER UNITED) in the EPL
